Historic Cybersecurity Breaches Caused by a Lack of Physical Security

### 2024-01-28 Paper/Paper.tex
More stuff

%%
%% This is file `sample-acmlarge.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `acmlarge')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-acmlarge.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{acmart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{acmart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[acmlarge]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmlicensed}
\copyrightyear{2024}
\begin{document}

@@

\author{Isaac Boaz}
\email{isaac.k.boaz@gmail.com}

@@

@@

Physical security is a part of cybersecurity. The act of protecting and
securing IT assets, data, and resources from physical attacks is a part
of cybersecurity. This article will review and analyze historical
occurences where a lack of physical security lead to a lack or even breach
of cybersecurity.

\section{Basic Physical Security}
Regardless of what a device is doing, it is always important to understand
the physical environment and security that the device is in. Even the
best anti-virus software cannot be protected from a malicious actor
uninstalling it. Physical access can mean a man in the middle attack,
power outages, or even a keylogger being installed.

Some basic physical security practices include:
\begin{itemize}
  \item Locking a device when not in use
  \item Restricting physical access to those that need it
  \item Locking the doors and windows of a building
  \item Scanning and limiting who can enter a building
\end{itemize}

@@

While not everyone that received the device plugged it in, it only took one of
Google's employees to plug it in for the attack be successful. The Red Team
gained unauthorized access to the documentation on Google's Glass, which
at the time was heavily in development.

@@

\subsection{Mitigation}
Google learned from this breach and created a software that would listen to extremely
fast keystrokes from USB devices and block them. This software was then installed
on all of Google's computers.

@@

\section{Mission Impossible}
A much more realistic example of a physical security breach is in the movie
Mission Impossible. In the movie, Ethan Hunt (played by Tom Cruise) is tasked
with stealing the NOC list from a CIA building. The NOC list is a list of all
CIA agents that are currently undercover. The CIA building is heavily guarded
and has many layers of security.

@@

Realistically, the CIA building should have had a more secure ventilation system;
we see that the team was able to get into the ventilation system (and the building itself)
by disguising as firefighers. The CIA did not have proper protocols or procedures
for fire alarms or drills, which allowed the team to easily enter the building.

@@

>>>>

\documentclass[acmsmall]{acmart}

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}
\setcopyright{acmlicensed}
\copyrightyear{2024}

\acmYear{2024}
\acmDOI{cybersecurity.tomcruise}
\acmJournal{TISSEC}
\acmVolume{420}
\acmNumber{69}
\acmArticle{3.14}
\acmMonth{1}

\setcopyright{acmlicensed}
\copyrightyear{2024}
\begin{document}

@@

\author{Isaac Boaz}
\email{boazi@wwu.edu}
\email{isaac.k.boaz@gmail.com}
\affiliation{%
  \institution{Western Washington University}
  \city{Seattle}
  \state{Washington}
  \country{USA}
}

@@

\begin{CCSXML}
  <ccs2012>
  <concept>
  <concept_id>10003456.10003462.10003561.10003563</concept_id>
  <concept_desc>Social and professional topics~Network access restrictions</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  <concept>
  <concept_id>10003456.10003462.10003561.10003566</concept_id>
  <concept_desc>Social and professional topics~Universal access</concept_desc>
  <concept_significance>100</concept_significance>
  </concept>
  <concept>
  <concept_id>10003456.10003462.10003574.10003000</concept_id>
  <concept_desc>Social and professional topics~Social engineering attacks</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10003456.10003462.10003574.10003578</concept_id>
  <concept_desc>Social and professional topics~Malware / spyware crime</concept_desc>
  <concept_significance>100</concept_significance>
  </concept>
  <concept>
  <concept_id>10002978.10002991</concept_id>
  <concept_desc>Security and privacy~Security services</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10002978.10003006</concept_id>
  <concept_desc>Security and privacy~Systems security</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Security and privacy~Security services}
\ccsdesc[500]{Security and privacy~Systems security}
\ccsdesc[300]{Social and professional topics~Network access restrictions}
\ccsdesc[500]{Social and professional topics~Social engineering attacks}
\ccsdesc[100]{Social and professional topics~Universal access}
\ccsdesc[100]{Social and professional topics~Malware / spyware crime}

@@

Physical security is a part of cybersecurity. The act of protecting and
securing IT assets, data, and resources from physical attacks is a part
of cybersecurity. This article will review and analyze both fictional and
non-fictional occurences where a lack of physical security lead to a lack
or breach of cybersecurity.

\section{Basic Physical Security}
Regardless of what a device is doing, it is always important to understand
the physical environment and security that the device is in. Even the
best anti-virus software cannot be protected from a malicious actor
uninstalling it. Physical access could mean a man in the middle attack,
power outages, or even a keylogger being installed.

Some basic physical security practices include:
\begin{itemize}
  \item Locking a device when not in use
  \item Restricting physical access to those that need it
  \item Locking the doors and windows of a building
  \item Scanning and limiting who can enter a building
  \item Ensuring that all devices are up to date
\end{itemize}

@@

While not everyone that received the device plugged it in, it only took one of
Google's employees to plug it in for the attack be successful. Upon successful
execution of the script, the Red Team had access to the employee's credentials.
Through this, they were able to send emails to other employees which had higher
privileges. Through these emails with attachments, the Red Team was able to
gain access to Google's Glasses internal documentation.

Finally, the Red Team attempted to obtain a physical build of the Google Glasses.
Unfortunately, due to a few typos, the Red Team caused a few red flags to be raised,
and instead of going to pick up the build, they were met with Google's Chief Security
Officer.

@@

\subsection{Mitigation}
Google learned from this breach and created a software that would listen to extremely
fast keystrokes from USB devices and block them. This software was then installed
on all of Google's computers, and publicly released \cite{Google02}.

@@

\section{Mission Impossible \texorpdfstring{\cite{missionimpossible}}{}}
A more realistic example of a physical security breach is in the movie
Mission Impossible. In the movie, Ethan Hunt (played by Tom Cruise) is tasked
with stealing the NOC list from a CIA building. The NOC list is a list of all
CIA agents that are currently undercover. The CIA building is heavily guarded
and has many layers of security.

@@

\subsection{Mitigation}
Realistically, the CIA building should have had a more secure ventilation system;
we see that the team was able to get into the ventilation system (and the building itself)
by disguising as firefighers. The CIA did not have proper protocols or procedures
for fire alarms or drills, which allowed the team to easily enter the building.

@@

\section{Conclusion}
We have seen examples of physical security and how attackers may navigate around
it. Being aware of all potential entrypoints and the human element of security is important
to keep in mind when designing a secure system. Security exploits could stem from the
design of a building (such as a server room being too accessible) to the training of
its employees.

Ensuring that all employees are trained to be aware of physical security and the dangers
of social engineering is important. Additionally, ensuring that all employees are trained
to be aware of the dangers of plugging in unauthorized devices is important. Having properly
defined protocols and procedures for unlikely events is also important.
Companies should internally test their security- GitLab for example similarly has a
"Red Team" that is tasked with trying to hack GitLab \cite{GitLab}.

\begin{acks}
  I would like to thank Google for their Plasma Globe attack, and the creators of
  Mission Impossible for their interesting portrayal of physical security.
\end{acks}
